Open Set Logo Detection and Retrieval

### 2017-09-06 paper-review.tex

\section{\uppercase{Logo Comparison}}
%TODO write text here

@@

For each search result, the first $N$ images are downloaded, where $N$ is determined by a quick manual inspection to avoid collecting too much garbage. 
%All search results are quickly inspected manually if a sufficient amount of suitable in-the-wild logo images is included and if so the first $N$ images are downloaded. 
After removing duplicates, this results in 4~to 574~images per searched brand. These images are then one-by-one manually annotated with logo bounding boxes or sorted out if unsuitable.
Images are considered unsuitable if they contain no logos or fail the in-the-wild requirement, which is the case for the original raw logo graphics. Taken pictures of such logos and advertisement posters on the other hand are desired to be in the dataset. 
Annotations distinguish between textual and graphical logos as well as different logos from one company as exemplary indicated in figure~\ref{fig:annotatedSample}.
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
\caption{Annotations differentiate between textual and graphical logos.}%
\label{fig:annotatedSample}
\end{figure}%
%
Altogether, the current version of the dataset, which is used in this paper, contains 872 brands with 32,850 annotated bounding boxes. 238 brands occur at least 10 times. An image may contain several logos with the maximum being 118 logos in one image. The complete distributions are shown in figures~\ref{fig:brandDistribution} and~\ref{fig:logoDistribution}. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 11cm 0cm 0cm, clip]{img/brandDistribution.pdf}%
\caption{Distribution of number of RoIs per brand.}%
\label{fig:brandDistribution}
\end{figure}%
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 11cm 0cm 0cm, clip]{img/logoDistribution.pdf}%
\caption{Distribution of number of RoIs per image.}%
\label{fig:logoDistribution}
\end{figure}%

>>>>

\section{\uppercase{Logo Comparison}}
%TODO write text here
After a logo is detected in an image, a correspondence from the query set should be searched. In order to retrieve as much objects from the images as possible, the detectors should work with a high recall. Although, for difficult tasks like open-set logo detection, high recall values induce usually a lot of false positive possible object locations. These examples should be eliminated by appropriate classifier. However, in case of image retrieval the goal is not direct classification, but rather feature extraction of a found region. Thus, the features of the logos of all the query images and the search set should be collected. The retrieved feature vectors are then normalized and the similarities of them are calculated with cosine similarity.
For baseline method, a Faster R-CNN is utilized, trained as usual. During inference, instead of detecting and classifying directly from the class probabilities, first the logos will be detected by processing the output of the RPN. Then, the class scores are used as discriminative feature for the underlying region. The feature vector of the query images are extracted from the complete image, since the logos fill the majority of these images.
Donahue et al. proposed \cite{donahue2015}, that convolutional networks can produce excellent descriptors of the input image, regardless of the absence of fine-tuning to the specific context of the image. For this purpose, a network is pretrained on very large datasets, after which it can be deployed for a broad set of computer vision problems. In our case, the networks were additionally fine-tuned with different amount of logo images.
The proposed logo retrieval system consists of a class agnostic logo detector and a feature extractor network. This setup is advantageous for the quality of the extracted features, because the complete network is only focused on a specific region.

@@

For each search result, the first $N$ images are downloaded, where $N$ is determined by a quick manual inspection to avoid collecting too much garbage. 
%All search results are quickly inspected manually if a sufficient amount of suitable in-the-wild logo images is included and if so the first $N$ images are downloaded. 
After removing duplicates, this results in 4~to 608~images per searched brand. These images are then one-by-one manually annotated with logo bounding boxes or sorted out if unsuitable.
Images are considered unsuitable if they contain no logos or fail the in-the-wild requirement, which is the case for the original raw logo graphics. Taken pictures of such logos and advertisement posters on the other hand are desired to be in the dataset. 
Annotations distinguish between textual and graphical logos as well as different logos from one company as exemplary indicated in figure~\ref{fig:annotatedSample}.
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 9cm 0cm 0cm, clip]{img/annotatedSample.pdf}%
\caption{Annotations differentiate between textual and graphical logos.}%
\label{fig:annotatedSample}
\end{figure}%
%
Altogether, the current version of the dataset, which is used in this paper, contains 872 brands with 32,850 annotated bounding boxes. 238 brands occur at least 10 times. An image may contain several logos with the maximum being 118 logos in one image. The complete distributions are shown in figures~\ref{fig:brandDistribution} and~\ref{fig:logoDistribution}. 
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 11cm 0cm 0cm, clip]{img/brandDistribution.pdf}%
\caption{Distribution of number of RoIs per brand.}%
\label{fig:brandDistribution}
\end{figure}%
%
\begin{figure}%
\centering%
\includegraphics[width=\linewidth, trim=0cm 11cm 0cm 0cm, clip]{img/logoDistribution.pdf}%
\caption{Distribution of number of RoIs per image.}%
\label{fig:logoDistribution}
\end{figure}%
